Cataclysmic variables are a key population of gravitational wave sources for LISA

### 2023-05-22 src/tex/ms.tex
fix abstract typo
fix abstract typo 2

% Abstract of the paper
\begin{abstract}

    AM~CVn stars are well established as an important population of gravitational wave (GW) sources for the planned \lisa\ mission. he less compact – but more numerous – cataclysmic variables (CVs) have not been studied carefully in this context. Here, we estimate the predicted GW signals from the Galactic population of cataclysmic variables and evaluate their significance for \lisa. First, we find that at least three known systems are expected to produce strong enough signals to be individually resolved within the first four years of \lisa's operation. Second, cataclysmic variables will contribute significantly to the \lisa\ Galactic binary background, thus limiting the mission's sensitivity in the relevant frequency band. Third, we predict a spike in the unresolved GW background at a frequency corresponding to the cataclysmic variable minimum orbital period. This excess noise may impact the detection of other low signal-to-noise systems near this characteristic frequency. Fourth, we note that the amplitude and location of the excess noise spike associated with $P_{\rm{min}}$ can be used to measure the cataclysmic variable space density and period bounce location with complementary and simple GW biases compared to the biases and selection effects that plague samples selected from electromagnetic signals. Our results highlight the need to explicitly include the Galactic cataclysmic variable population in \lisa\ mission planning, both as individual GW sources and generators of background noise, as well as the exciting prospect of characterising the cataclysmic variable population through their GW emission.
\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}
AM~CVn stars are well established as an important population of gravitational wave (GW) sources for the planned \lisa\ mission. The less compact – but more numerous – cataclysmic variables (CVs) have not been studied carefully in this context. Here, we estimate the predicted GW signals from the Galactic population of cataclysmic variables and evaluate their significance for \lisa. First, we find that at least three known systems are expected to produce strong enough signals to be individually resolved within the first four years of \lisa's operation. Second, cataclysmic variables will contribute significantly to the \lisa\ Galactic binary background, thus limiting the mission's sensitivity in the relevant frequency band. Third, we predict a spike in the unresolved GW background at a frequency corresponding to the cataclysmic variable minimum orbital period. This excess noise may impact the detection of other low signal-to-noise systems near this characteristic frequency. Fourth, we note that the amplitude and location of the excess noise spike associated with $P_{\rm{min}}$ can be used to measure the cataclysmic variable space density and period bounce location with complementary and simple GW biases compared to the biases and selection effects that plague samples selected from electromagnetic signals. Our results highlight the need to explicitly include the Galactic cataclysmic variable population in \lisa\ mission planning, both as individual GW sources and generators of background noise, as well as the exciting prospect of characterising the cataclysmic variable population through their GW emission.
\end{abstract}
